### 2018-04-30 paper/message-passing-design.tex
readded comments

\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Send}{BuildRouteS}
\NewAlgorithm{\Recv}{BuildRouteR}
\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\CreateOnionLayer}{CreateLayer}
\NewAlgorithm{\Dec}{Dec}
\NewAlgorithm{\Store}{Store}
\NewVariable{\sk}{sk}
\NewVariable{\rdv}{rdv}
\NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\xspace}
\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\xspace}
\NewVariable{\Hforward}{\mathcal{H}_f \xspace}
\NewVariable{\Hbackward}{\mathcal{H}_b \xspace}
\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send f}}\xspace}
\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send b}}\xspace}
\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec f}}\xspace}
\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec b}}\xspace}
%\NewVariable{\nfilechunks}{\#\text{chunks}}

\david{each protocol should be explained individually}

@@

\paragraph*{Layer creation}
The function \CreateOnionLayer() iteratively add random nodes (from the RPS's view \view) until the product $\prod_{d\in \mathcal{L}} (1 - p_d)$ falls below $\theta$.
$(1 - p_d)$ is the probability that a device $d$ will be offline; the product is the probability that all devices on layer $\mathcal{L}$ fall offline at the same time.

>>>>

\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Send}{BuildRouteS}
\NewAlgorithm{\Recv}{BuildRouteR}
\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\CreateOnionLayer}{CreateLayer}
\NewAlgorithm{\Dec}{Dec}
\NewAlgorithm{\Store}{Store}
\NewVariable{\sk}{sk}
\NewVariable{\rdv}{rdv}
\NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\xspace}
\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\xspace}
\NewVariable{\Hforward}{\mathcal{H}_f\xspace}
\NewVariable{\Hbackward}{\mathcal{H}_b\xspace}
\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send f}}\xspace}
\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send b}}\xspace}
\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec f}}\xspace}
\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec b}}\xspace}
%\NewVariable{\nfilechunks}{\#\text{chunks}}

@@

\paragraph*{Layer creation}
The function \CreateOnionLayer() iteratively adds random nodes (from the RPS's view \view) until the product $\prod_{d\in \mathcal{L}} (1 - p_d)$ falls below $\theta$.
$(1 - p_d)$ is the probability that a device $d$ will be offline; the product is the probability that all devices on layer $\mathcal{L}$ fall offline at the same time.
